This is the title [Article v\versionnumber]

### 2019-11-04 templates/livecoms-template-bestpractices.tex
Mild grammatical changes

Additionally, for well-formatted manuscripts, we recommend that you let LaTeX handle figure/table placement for you as much as possible, so avoiding specifying strenuous float instructions like `[h!]` and `[H]` as much as possible.

>>>>

Additionally, for well-formatted manuscripts, we recommend that you let LaTeX handle figure/table placement for you as much as possible, so please avoid specifying strenuous float instructions like `[h!]` and `[H]` as much as possible.
